\documentclass[15pt]{article}

% load packages
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18} 
\usepackage{multirow,array} % for payoff matrix formatting
% use exsheets to create different versions with \vary{}{}
\usepackage{exsheets}
\SetupExSheets{
  headings = block-wp,
  solution/print = false % set this to true to print key
}

% document formatting settings
\geometry{left=1.0in,right=1.0in,top=0.75in,bottom=1.0in}
\setlength{\parindent}{0pt} % turn off para indenting

% title and date for cover page
\title{
    \textbf{Econ 311 - Intermediate Microeconomics} \\ 
    Midterm Exam
    }
\author{University of Oregon}
\date{April 30, 2025}

% DOCUMENT BEGINS HERE
\begin{document}

\maketitle

% SET VERSION NUMBER HERE: 
\variant{1}

\begin{center}
  \Large{\textbf{Version \vary{1}{2}}}
\end{center}

\begin{center}
  \fbox{\fbox{\parbox{4in}{\centering
    Give every question your best shot. \\
    Never back down. Never what? \\
    Never Give Up.}}}
\end{center}

\vspace{0.5in}

% space for student to write their name
\makebox[.6\textwidth]{Name: \enspace\hrulefill} \makebox[.3\textwidth]{95\#: \enspace\hrulefill}

\vspace{0.5in}

% instructions section
You have a total of 1h 50min (110 minutes) to complete the exam.

The only items allowed on your desk at any time are pens/pencils, scratch paper, a 3x5 note card, and a calculator. Everything else must be stored in your bag underneath your desk.

If you need to use the bathroom during the exam, leave your phone on the table in the front of the classroom. Please wait until there are no phones currently on the table before you go to the bathroom.

Any form of cheating will result on a zero on the exam.

\vspace{0.25in}

There are three sections to be completed:
\begin{itemize}
  \item Multiple Choice: 10 Questions
  \item Short-Answer Questions: 4 Questions
  \item Multi-Part Analysis Questions: 2 Questions
\end{itemize}

\vspace{0.25in}

Point totals and question specific instructions are listed for each section.
Please ask for clarification if a question is not clear to you.

\vspace{0.25in}

The exam is a total of 8 pages.
Please verify you have all 8 in your exam. 
If you do not, let me know immediately.

\newpage

%------------------------------------------------------------------------------%

\section*{Multiple Choice}

\input{questions/mc}

%------------------------------------------------------------------------------%
\newpage

\section*{Short Answer}

\input{questions/bundles}
\vspace{5cm}

\input{questions/util-func}
\vspace{5cm}

\newpage

\input{questions/p-elas-d}
\vspace{5cm}

\input{questions/mrs}
\vspace{5cm}

\newpage

%------------------------------------------------------------------------------%
\newpage

\section*{Long Answer}

\input{questions/long-subeffect}

\newpage

\input{questions/long-demand}

\newpage


%------------------------------------------------------------------------------%


\end{document}
